Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-22 paper.qmd

XXX Prediction should have a jitter option, to spread the predicted points out fully in the hexagons.

@@

<!--To generate errors for different total number of bins-->
```{r}
## To initialize number of bins along the x-axis
bin1_vec_scurve <- 2:19 #sqrt(NROW(training_data_scurve)/2)
buffer_vec <- seq(0.05, 0.1, by = 0.01)

>>>>

<!-- XXX Prediction should have a jitter option, to spread the predicted points out fully in the hexagons. -->

@@

<!--To generate errors for different total number of bins-->
```{r}
#| eval: false
## To initialize number of bins along the x-axis
bin1_vec_scurve <- 2:19 #sqrt(NROW(training_data_scurve)/2)
buffer_vec <- seq(0.05, 0.1, by = 0.01)
